\documentclass[conference]{IEEEtran}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{array, listings, color, todonotes, amsmath}
\usepackage[bookmarks=false]{hyperref}

\usepackage{graphicx,times,amsmath} % Add all your packages here

\hyphenation{op-tical net-works semi-conduc-tor IEEEtran}

\IEEEoverridecommandlockouts    % to create the author's affliation portion
                % using \thanks

\textwidth 178mm    % <------ These are the adjustments we made 10/18/2005
\textheight 239mm   % You may or may not need to adjust these numbers again
\oddsidemargin -7mm
\evensidemargin -7mm
\topmargin -6mm
\columnsep 5mm

\begin{document}

\title{The 2013 Multi-objective Physical Travelling Salesman Problem Competition \thanks{Diego Perez, Spyridon Samothrakis and Simon Lucas are with the School of Computer Science and Electronic Engineering of the University of Essex (email: \{dperez, ssamot, sml\}@essex.ac.uk).} \thanks{Edward Powley, Daniel Whitehouse and Peter Cowling are with the Computer Science department of the University of York (email:  \{edward.powley, dw830, peter.cowling\}@york.ac.uk).} \thanks{This work was supported by EPSRC grant EP/H048588/1.}}

\author{Diego Perez, Edward Powley, Daniel Whitehouse, Spyridon Samothrakis, Simon Lucas, Peter Cowling}


% make the title area
\maketitle

\begin{abstract}
Numerous competitions have emerged in recent years... and this is another one.
\end{abstract}

% no key words

\section{Introduction}

Research in games and competitions.
Literature review~\cite{PerezCEC2012,MCTSSurvey}.

\section{The Multi-objective Travelling Salesman Problem}

Description of the game: physics, constraints.
Description of maps: dimensions, specifications.

\section{The MO-PTSP Competition}

Infrastructure of the competition, rules, how entries are ranked.
Evaluation, submission, programming specification, API.
Sample controllers: random, greedy, macro-action random search controller. Include some measurements.

\section{The winning entry}

\todo[inline]{Description: York.}

\section{Results of the competition}

Describe results in detail.

\section{Conclusions}

All was very fun.

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,biblio}

\end{document}
